
## Environment

```{r}
library(tidyverse)
library(patchwork)
library(rstatix)
library(ggbeeswarm)
library(furrr)
library(ggprism)

plan(multisession, workers = 8)
```

## Using esg and Toll (12d) (box plot with w1118 and Toll10b)

```{r}
## Clean up
output_files <- list.files("/Users/jefflee/Documents/Github/Image-analysis/people/Ash_U/output/combined_first_second_df", 
                           pattern = "*.csv", 
                           full.names = TRUE) %>%
  set_names(~basename(.x) %>% tools::file_path_sans_ext())

df_raw <- output_files %>%
  future_map_dfr(~ read_csv(.x), .id = "filename", .progress = TRUE) 

df_annotated <- df_raw %>%
  janitor::clean_names() %>%
  dplyr::select(-x1) %>%
  mutate(genotype = case_when(
    str_detect(filename, "esg") ~ "esg",
    str_detect(filename, "toll") ~ "toll",
    str_detect(filename, "bsk") ~ "bsk",
    TRUE ~ "Unidentified"
  )) %>%
  mutate(age = str_extract(filename, "[:digit:]+d")) %>%
  mutate(age = case_when(
    age == "22d" ~ "22d",
    TRUE ~ "12d"
  )) %>%
  mutate(experiment = str_extract(filename, "exp[:upper:]")) %>%
  mutate(GFP_intensity_density = gfp_intensity_sum / doughnut_area) %>%
  dplyr::rename("centroid_z" = centroid_0, "centroid_y" = centroid_1, "centroid_x" = centroid_2)

## Set nuclear size threshold
df_annotated %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = axis_major_length)) + 
  geom_vline(xintercept = 7, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 14, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 17.5, linetype = "dashed", alpha = 0.5) + 
  geom_density() + 
  theme_bw() +
  facet_wrap(~ experiment + age)

df_nucsize <- df_annotated %>%
  filter(axis_major_length > 2) %>%
  mutate(nuclear_size = if_else(axis_major_length > 17.5, "large", "small"))

## Set GFP threshold
esg_GFP_control <- df_nucsize %>%
  filter(genotype == "esg") %>%
  group_by(experiment, nuclear_size, age) %>%
  summarise(esg_GFP_density = mean(GFP_intensity_density, na.rm = TRUE)) %>%
  ungroup()

df_GFPnorm <- df_nucsize %>%
  left_join(esg_GFP_control, by = c("experiment", "nuclear_size", "age")) %>%
  mutate(norm_GFP_intensity_density = GFP_intensity_density / esg_GFP_density) %>%
  mutate(genotype = fct_relevel(genotype, c("esg", "toll", "bsk"))) %>%
  mutate(nuclear_size = fct_relevel(nuclear_size, c("small", "large")))

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density)) +
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = 2) + 
  facet_wrap(~ experiment) 

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density, y = axis_major_length)) +
  geom_point() + 
  geom_vline(xintercept = 1.25) + 
  facet_wrap(~ experiment) 

df_GFPnorm_thresholded <- df_GFPnorm %>%
  filter(!(nuclear_size == "small" & norm_GFP_intensity_density < 1.25)) %>%
  mutate(GFP_positive = if_else(norm_GFP_intensity_density > 1.5, TRUE, FALSE))

df_existing <- df_GFPnorm_thresholded

```

### GFP+ cells/ Total cells

```{r}
df <- df_GFPnorm_thresholded %>%
  filter(age == "12d") %>%
  filter(!str_detect(genotype, "bsk")) %>%
  group_by(filename, genotype) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive)
  ) %>%
  ungroup() %>%
  mutate(GFPpos_pct = GFPpos_cellcount / total_cellcount * 100) 

stat <- df %>%
  t_test(GFPpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = GFPpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "GFP+ cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "coral")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_01/esg_toll_GFPpos.pdf", width = 5.5, height = 5)

```

### Small nuclei GFP+ cells/ total small nuclei cells

```{r}
df <- df_existing %>%
  filter(age == "12d") %>%
  filter(!str_detect(genotype, "bsk")) %>%
  filter(nuclear_size == "small") %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive)
  ) %>%
  ungroup() %>%
  mutate(GFPpos_pct = GFPpos_cellcount / total_cellcount * 100) 

  View(df)

stat <- df %>%
  t_test(GFPpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = GFPpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "GFP+ small nuclei cells / Total small nuclei cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "coral")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_01/esg_toll_GFPpos_smallnuc.pdf", width = 5.5, height = 5)
```

### Big nuceli GFP+ cell/ Total big nuclei cells.

```{r}
df <- df_GFPnorm_thresholded %>%
  filter(age == "12d") %>%
  filter(!str_detect(genotype, "bsk")) %>%
  filter(nuclear_size == "large") %>%
  group_by(filename, genotype) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive)
  ) %>%
  ungroup() %>%
  mutate(GFPpos_pct = GFPpos_cellcount / total_cellcount * 100) 

stat <- df %>%
  t_test(GFPpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = GFPpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "GFP+ large nuclei cells / Total large nuclei cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "coral")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_01/esg_toll_GFPpos_largenuc.pdf", width = 5.5, height = 5)
```

### Small nuclei/total

```{r}
df <- df_GFPnorm_thresholded %>%
  filter(age == "12d") %>%
  filter(!str_detect(genotype, "bsk")) %>%
  group_by(filename, genotype) %>%
  summarise(
    total_cellcount = n(),
    smallnuc_cellcount = sum(nuclear_size == "small")
  ) %>%
  ungroup() %>%
  mutate(smallnuc_pct = smallnuc_cellcount / total_cellcount * 100) 

stat <- df %>%
  t_test(smallnuc_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = smallnuc_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Small nuclei cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "coral")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_01/esg_toll_smallnuc_pct.pdf", width = 5.5, height = 5)
```

### Big nuclei total

```{r}
df <- df_GFPnorm_thresholded %>%
  filter(age == "12d") %>%
  filter(!str_detect(genotype, "bsk")) %>%
  group_by(filename, genotype) %>%
  summarise(
    total_cellcount = n(),
    largenuc_cellcount = sum(nuclear_size == "large")
  ) %>%
  ungroup() %>%
  mutate(largenuc_pct = largenuc_cellcount / total_cellcount * 100) 

stat <- df %>%
  t_test(largenuc_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = largenuc_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Large nuclei cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "coral")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_01/esg_toll_largenuc_pct.pdf", width = 5.5, height = 5)
```

## Using esg , Toll and bskDN(12d)----Already given data Keep the already existing graphs,

### GFP+ cells/ Total cells

```{r}
df <- df_GFPnorm_thresholded %>%
  filter(age == "12d") %>%
  group_by(filename, genotype) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive)
  ) %>%
  ungroup() %>%
  mutate(GFPpos_pct = GFPpos_cellcount / total_cellcount * 100) 

stat <- df %>%
  tukey_hsd(GFPpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = GFPpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "GFP+ cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "steelblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    bsk = expression(Toll^"10b" + Bsk^"DN")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_02/esg_toll_bsk_GFPpos.pdf", width = 5.5, height = 5)
```

### Small nuclei GFP+ cells/ total small nuclei cells

```{r}
df <- df_GFPnorm_thresholded %>%
  filter(age == "12d") %>%
  group_by(filename, genotype) %>%
  filter(nuclear_size == "small") %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive)
  ) %>%
  ungroup() %>%
  mutate(GFPpos_pct = GFPpos_cellcount / total_cellcount * 100) 

stat <- df %>%
  tukey_hsd(GFPpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = GFPpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "GFP+ small nuclei cells / Total small nuclei cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "steelblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    bsk = expression(Toll^"10b" + Bsk^"DN")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_02/esg_toll_bsk_GFPpos_smallnuc.pdf", width = 5.5, height = 5)
```

### Big nuceli GFP+ cell/ Total big nuclei cells.

```{r}
df <- df_GFPnorm_thresholded %>%
  filter(age == "12d") %>%
  group_by(filename, genotype) %>%
  filter(nuclear_size == "large") %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive)
  ) %>%
  ungroup() %>%
  mutate(GFPpos_pct = GFPpos_cellcount / total_cellcount * 100) 

stat <- df %>%
  tukey_hsd(GFPpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = GFPpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "GFP+ large nuclei cells / Total large nuclei cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "steelblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    bsk = expression(Toll^"10b" + Bsk^"DN")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_02/esg_toll_bsk_GFPpos_largenuc.pdf", width = 5.5, height = 5)
```

### Small nuclei/total

```{r}
df <- df_GFPnorm_thresholded %>%
  filter(age == "12d") %>%
  group_by(filename, genotype) %>%
  summarise(
    total_cellcount = n(),
    smallnuc_cellcount = sum(nuclear_size == "small")
  ) %>%
  ungroup() %>%
  mutate(smallnuc_pct = smallnuc_cellcount / total_cellcount * 100) 

stat <- df %>%
  tukey_hsd(smallnuc_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = smallnuc_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Small nuclei cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "steelblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    bsk = expression(Toll^"10b" + Bsk^"DN")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_02/esg_toll_bsk_smallnuc.pdf", width = 5.5, height = 5)
```

### Big nuclei total

```{r}
df <- df_GFPnorm_thresholded %>%
  filter(age == "12d") %>%
  group_by(filename, genotype) %>%
  summarise(
    total_cellcount = n(),
    largenuc_cellcount = sum(nuclear_size == "large")
  ) %>%
  ungroup() %>%
  mutate(largenuc_pct = largenuc_cellcount / total_cellcount * 100) 

stat <- df %>%
  tukey_hsd(largenuc_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = largenuc_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Large nuclei cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "steelblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    bsk = expression(Toll^"10b" + Bsk^"DN")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_02/esg_toll_bsk_largenuc.pdf", width = 5.5, height = 5)
```


## Pros folder 03

```{r}
process_files <- function(output_dir, exp_name) {
    output_files_A <- list.files(
        output_dir,
        pattern = "*.csv",
        full.names = TRUE
    ) %>%
        set_names(~ basename(.x) %>% tools::file_path_sans_ext())

    df_annotated <- output_files_A %>%
        future_map_dfr(~ read_csv(.x), .id = "filename", .progress = TRUE) %>%
        janitor::clean_names() %>%
        dplyr::select(-x1) %>%
        mutate(genotype = case_when(
            str_detect(filename, "toll") ~ "toll",
            str_detect(filename, "bsk") ~ "bsk",
            str_detect(filename, "esg") ~ "esg",
            TRUE ~ "NA"
        )) %>%
        mutate(age = str_extract(filename, "[:digit:]+d")) %>%
        mutate(age = case_when(
            age == "22d" ~ "22d",
            TRUE ~ "12d"
        )) %>%
        mutate(GFP_intensity_density = gfp_intensity_sum / doughnut_area) %>%
        dplyr::rename("centroid_z" = centroid_0, "centroid_y" = centroid_1, "centroid_x" = centroid_2) %>%
        mutate(experiment = exp_name)
}
```

### Data wrangling

```{r}
##
df_annotated_A <- process_files("/Users/jefflee/Desktop/for_ash_13sep/pros/1/output_df", "expA") %>%
  mutate(pros_intensity_density = other_intensity_sum / area)

df_annotated_B <- process_files("/Users/jefflee/Desktop/for_ash_13sep/pros/2/output_df", "expB") %>%
  mutate(pros_intensity_density = other_intensity_sum / area)

df_annotated <- bind_rows(df_annotated_A, df_annotated_B)

## Set nuclear size threshold
df_annotated %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = axis_major_length)) + 
  geom_vline(xintercept = 7, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 14, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 17.5, linetype = "dashed", alpha = 0.5) + 
  geom_density() + 
  theme_bw() +
  facet_wrap(~ experiment + age)

df_nucsize <- df_annotated %>%
  filter(axis_major_length > 2) %>%
  mutate(nuclear_size = if_else(axis_major_length > 17.5, "large", "small"))

## Set GFP threshold
esg_GFP_control <- df_nucsize %>%
  filter(genotype == "esg") %>%
  group_by(experiment, nuclear_size, age) %>%
  summarise(esg_GFP_density = mean(GFP_intensity_density, na.rm = TRUE)) %>%
  ungroup()

df_GFPnorm <- df_nucsize %>%
  left_join(esg_GFP_control, by = c("experiment", "nuclear_size", "age")) %>%
  mutate(norm_GFP_intensity_density = GFP_intensity_density / esg_GFP_density) %>%
  mutate(genotype = fct_relevel(genotype, c("esg", "toll", "bsk"))) %>%
  mutate(nuclear_size = fct_relevel(nuclear_size, c("small", "large")))

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density)) +
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = 2) + 
  facet_wrap(~ experiment) 

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density, y = axis_major_length)) +
  geom_point() + 
  geom_vline(xintercept = 1.25) + 
  facet_wrap(~ experiment) 

df_GFPnorm_thresholded <- df_GFPnorm %>%
  filter(!(nuclear_size == "small" & norm_GFP_intensity_density < 1.25)) %>%
  mutate(GFP_positive = if_else(norm_GFP_intensity_density > 1.5, TRUE, FALSE))

## Set pros threshold
esg_pros_control <- df_GFPnorm_thresholded %>%
  filter(genotype == "esg") %>%
  group_by(experiment, nuclear_size, age) %>%
  summarise(esg_pros_density = mean(pros_intensity_density, na.rm = TRUE)) %>%
  ungroup()

df_prosnorm <- df_GFPnorm_thresholded %>%
  left_join(esg_pros_control, by = c("experiment", "nuclear_size", "age")) %>%
  mutate(norm_pros_intensity_density = pros_intensity_density / esg_pros_density) %>%
  mutate(genotype = fct_relevel(genotype, c("esg", "toll", "bsk"))) %>%
  mutate(nuclear_size = fct_relevel(nuclear_size, c("small", "large")))

df_prosnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_pros_intensity_density)) +
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = 2) + 
  facet_wrap(~ experiment) 

df_prosnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_pros_intensity_density, y = axis_major_length)) +
  geom_point() + 
  geom_vline(xintercept = 1.5) + 
  facet_wrap(~ experiment) 

df_prosnorm_thresholded <- df_prosnorm %>%
  mutate(pros_positive = if_else(norm_pros_intensity_density > 1.5, TRUE, FALSE))


```

### Pros+ cells per total cells

```{r}
df <- df_prosnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive),
    Prospos_cellcount = sum(pros_positive),
    Prospos_GFPpos_cellcount = sum(pros_positive == TRUE & GFP_positive == TRUE),
    Prospos_GFPneg_cellcount = sum(pros_positive == TRUE & GFP_positive == FALSE),
  ) %>%
  ungroup() %>%
  mutate(
    GFPpos_pct = GFPpos_cellcount / total_cellcount * 100,
    Prospos_pct = Prospos_cellcount / total_cellcount * 100,
    Prospos_GFPpos_pct = Prospos_GFPpos_cellcount / total_cellcount * 100,
    Prospos_GFPneg_pct = Prospos_GFPneg_cellcount / total_cellcount * 100,
    ) 

stat <- df %>%
  t_test(Prospos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = Prospos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Pros+ cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "coral")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_03/Prospos-per-totalcells.pdf", width = 5.5, height = 5)
```

### Pros+ & GFP+ cells 

```{r}
df <- df_prosnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive),
    Prospos_cellcount = sum(pros_positive),
    Prospos_GFPpos_cellcount = sum(pros_positive == TRUE & GFP_positive == TRUE),
    Prospos_GFPneg_cellcount = sum(pros_positive == TRUE & GFP_positive == FALSE),
  ) %>%
  ungroup() %>%
  mutate(
    GFPpos_pct = GFPpos_cellcount / total_cellcount * 100,
    Prospos_pct = Prospos_cellcount / total_cellcount * 100,
    Prospos_GFPpos_pct = Prospos_GFPpos_cellcount / total_cellcount * 100,
    Prospos_GFPneg_pct = Prospos_GFPneg_cellcount / total_cellcount * 100,
    ) 

stat <- df %>%
  t_test(Prospos_GFPpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = Prospos_GFPpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Pros+ & GFP+ cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "coral")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_03/Prospos_GFPpos-per-totalcells.pdf", width = 5.5, height = 5)
```

### Pros+ & GFP- cells

```{r}
df <- df_prosnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive),
    Prospos_cellcount = sum(pros_positive),
    Prospos_GFPpos_cellcount = sum(pros_positive == TRUE & GFP_positive == TRUE),
    Prospos_GFPneg_cellcount = sum(pros_positive == TRUE & GFP_positive == FALSE),
  ) %>%
  ungroup() %>%
  mutate(
    GFPpos_pct = GFPpos_cellcount / total_cellcount * 100,
    Prospos_pct = Prospos_cellcount / total_cellcount * 100,
    Prospos_GFPpos_pct = Prospos_GFPpos_cellcount / total_cellcount * 100,
    Prospos_GFPneg_pct = Prospos_GFPneg_cellcount / total_cellcount * 100,
    ) 

stat <- df %>%
  t_test(Prospos_GFPneg_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = Prospos_GFPneg_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Pros+ & GFP- cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "coral")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_03/Prospos_GFPneg-per-totalcells.pdf", width = 5.5, height = 5)
```

### Pros+/GFP+ out of Pros+ 

```{r}
df <- df_prosnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive),
    Prospos_cellcount = sum(pros_positive),
    Prospos_GFPpos_cellcount = sum(pros_positive == TRUE & GFP_positive == TRUE),
    Prospos_GFPneg_cellcount = sum(pros_positive == TRUE & GFP_positive == FALSE),
  ) %>%
  ungroup() %>%
  mutate(
    GFPpos_pct = GFPpos_cellcount / total_cellcount * 100,
    Prospos_pct = Prospos_cellcount / total_cellcount * 100,
    Prospos_GFPpos_pct = Prospos_GFPpos_cellcount / total_cellcount * 100,
    Prospos_GFPpos_pct_Pros = Prospos_GFPpos_cellcount / Prospos_cellcount * 100,
    Prospos_GFPneg_pct = Prospos_GFPneg_cellcount / total_cellcount * 100,
    ) 

stat <- df %>%
  t_test(Prospos_GFPpos_pct_Pros ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = Prospos_GFPpos_pct_Pros, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Pros+ & GFP+ cells / Pros+ cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "coral")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_03/Prospos_GFPpos-per-Prospos-cellcount.pdf", width = 5.5, height = 5)
```

## Toll dif RNAi folder 04

### Data wrangling

```{r}
## Existing toll
df_existing_toll <- df_existing %>%
  filter(genotype == "toll")

##
df_annotated_A <- process_files("/Users/jefflee/Desktop/for_ash_13sep/toll-difrnai/1/output_df", "expA") %>%
  mutate(pros_intensity_density = other_intensity_sum / area)
df_annotated_B <- process_files("/Users/jefflee/Desktop/for_ash_13sep/toll-difrnai/2/output_df", "expB") %>%
  mutate(pros_intensity_density = other_intensity_sum / area)
df_annotated_C <- process_files("/Users/jefflee/Desktop/for_ash_13sep/toll-difrnai/3/output_df", "expC") %>%
  mutate(pros_intensity_density = other_intensity_sum / area)

df_annotated <- bind_rows(df_annotated_A, df_annotated_B, df_annotated_C) %>%
  mutate(genotype = if_else(genotype == "toll", "tolldif", genotype))

## Set nuclear size threshold
df_annotated %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = axis_major_length)) + 
  geom_vline(xintercept = 7, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 14, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 17.5, linetype = "dashed", alpha = 0.5) + 
  geom_density() + 
  theme_bw() +
  facet_wrap(~ experiment + age)

df_nucsize <- df_annotated %>%
  filter(axis_major_length > 2) %>%
  mutate(nuclear_size = if_else(axis_major_length > 17.5, "large", "small"))

## Set GFP threshold
esg_GFP_control <- df_nucsize %>%
  filter(genotype == "esg") %>%
  group_by(experiment, nuclear_size, age) %>%
  summarise(esg_GFP_density = mean(GFP_intensity_density, na.rm = TRUE)) %>%
  ungroup()

df_GFPnorm <- df_nucsize %>%
  left_join(esg_GFP_control, by = c("experiment", "nuclear_size", "age")) %>%
  mutate(norm_GFP_intensity_density = GFP_intensity_density / esg_GFP_density) %>%
#   mutate(genotype = fct_relevel(genotype, c("esg", "toll", "bsk"))) %>%
  mutate(nuclear_size = fct_relevel(nuclear_size, c("small", "large")))

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density)) +
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = 2) + 
  facet_wrap(~ experiment) 

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density, y = axis_major_length)) +
  geom_point() + 
  geom_vline(xintercept = 1.25) + 
  facet_wrap(~ experiment) 

df_GFPnorm_thresholded <- df_GFPnorm %>%
  filter(!(nuclear_size == "small" & norm_GFP_intensity_density < 1.25)) %>%
  mutate(GFP_positive = if_else(norm_GFP_intensity_density > 1.5, TRUE, FALSE))


df_GFPnorm_thresholded <- bind_rows(df_GFPnorm_thresholded, df_existing_toll)

```

### GFP+ cells per total

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive)
  ) %>%
  ungroup() %>%
  mutate(GFPpos_pct = GFPpos_cellcount / total_cellcount * 100) 

stat <- df %>%
  tukey_hsd(GFPpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = GFPpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "GFP+ cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "red")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    tolldif = expression(Toll^"10b" + Dif^"RNAi")

  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_04/esg-toll-tolldif_GFPpos.pdf", width = 5.5, height = 5)
```

### Total cells

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive)
  ) %>%
  ungroup() %>%
  mutate(GFPpos_pct = GFPpos_cellcount / total_cellcount * 100) 

stat <- df %>%
  tukey_hsd(total_cellcount ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = total_cellcount, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Total cell counts",
    x = "Genotype",
    y = "Cell count"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "red")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    tolldif = expression(Toll^"10b" + Dif^"RNAi")

  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_04/esg-toll-tolldif_total-cellcount.pdf", width = 5.5, height = 5)
```

### Large cells per total

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype) %>%
  summarise(
    total_cellcount = n(),
    largenuc_cellcount = sum(nuclear_size == "large")
  ) %>%
  ungroup() %>%
  mutate(largenuc_pct = largenuc_cellcount / total_cellcount * 100) 

stat <- df %>%
  tukey_hsd(largenuc_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = largenuc_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "large nuclei cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "red")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    tolldif = expression(Toll^"10b" + Dif^"RNAi")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_04/esg-toll-tolldif_largenuc.pdf", width = 5.5, height = 5)
```

### Small cells per total

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype) %>%
  summarise(
    total_cellcount = n(),
    smallnuc_cellcount = sum(nuclear_size == "small")
  ) %>%
  ungroup() %>%
  mutate(smallnuc_pct = smallnuc_cellcount / total_cellcount * 100) 

stat <- df %>%
  tukey_hsd(smallnuc_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = smallnuc_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Small nuclei cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "red")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    tolldif = expression(Toll^"10b" + Dif^"RNAi")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_04/esg-toll-tolldif_smallnuc.pdf", width = 5.5, height = 5)

```

## Cactus RNAi folder 05

### Data wrangling

```{r}
## Existing toll
df_existing_toll <- df_existing %>%
  mutate(genotype = as.character(genotype)) %>%
  filter(genotype == "toll")

df_existing_toll$genotype %>% unique()


##
df_annotated_A <- process_files("/Users/jefflee/Desktop/for_ash_13sep/cactusrnai/1/output_df", "expA")
df_annotated_B <- process_files("/Users/jefflee/Desktop/for_ash_13sep/cactusrnai/2/output_df", "expB") 

df_annotated <- bind_rows(df_annotated_A, df_annotated_B) %>%
  mutate(genotype = if_else(str_detect(filename, "cactus"), "cactus", genotype))

df_annotated$genotype %>% unique()

## Set nuclear size threshold
df_annotated %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = axis_major_length)) + 
  geom_vline(xintercept = 7, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 14, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 17.5, linetype = "dashed", alpha = 0.5) + 
  geom_density() + 
  theme_bw() +
  facet_wrap(~ experiment + age)

df_nucsize <- df_annotated %>%
  filter(axis_major_length > 2) %>%
  mutate(nuclear_size = if_else(axis_major_length > 17.5, "large", "small"))

## Set GFP threshold
esg_GFP_control <- df_nucsize %>%
  filter(genotype == "esg") %>%
  group_by(experiment, nuclear_size, age) %>%
  summarise(esg_GFP_density = mean(GFP_intensity_density, na.rm = TRUE)) %>%
  ungroup()

df_GFPnorm <- df_nucsize %>%
  left_join(esg_GFP_control, by = c("experiment", "nuclear_size", "age")) %>%
  mutate(norm_GFP_intensity_density = GFP_intensity_density / esg_GFP_density) %>%
#   mutate(genotype = fct_relevel(genotype, c("esg", "toll", "bsk"))) %>%
  mutate(nuclear_size = fct_relevel(nuclear_size, c("small", "large")))

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density)) +
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = 2) + 
  facet_wrap(~ experiment) 

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density, y = axis_major_length)) +
  geom_point() + 
  geom_vline(xintercept = 1.25) + 
  facet_wrap(~ experiment) 

df_GFPnorm_thresholded <- df_GFPnorm %>%
  filter(!(nuclear_size == "small" & norm_GFP_intensity_density < 1.25)) %>%
  mutate(GFP_positive = if_else(norm_GFP_intensity_density > 1.5, TRUE, FALSE))

df_GFPnorm_thresholded$genotype %>% unique()

df_GFPnorm_thresholded <- bind_rows(df_GFPnorm_thresholded, df_existing_toll)

df_GFPnorm_thresholded$genotype %>% unique()

```

### GFP+ cells per total

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive)
  ) %>%
  ungroup() %>%
  mutate(GFPpos_pct = GFPpos_cellcount / total_cellcount * 100) %>%
  mutate(genotype = fct_relevel(genotype, c("esg", "toll", "cactus")))

stat <- df %>%
  tukey_hsd(GFPpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = GFPpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "GFP+ cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "skyblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    cactus = expression(Cactus^"RNAi")

  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_05/esg-toll-cactus_GFPpos.pdf", width = 5.5, height = 5)
```

### Total cells

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive)
  ) %>%
  ungroup() %>%
  mutate(GFPpos_pct = GFPpos_cellcount / total_cellcount * 100) %>%
  mutate(genotype = fct_relevel(genotype, c("esg", "toll", "cactus")))

stat <- df %>%
  tukey_hsd(total_cellcount ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = total_cellcount, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Total cell counts",
    x = "Genotype",
    y = "Cell count"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "skyblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    cactus = expression(Cactus^"RNAi")

  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_05/esg-toll-cactus_total-cellcount.pdf", width = 5.5, height = 5)
```

### Large cells per total

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype) %>%
  summarise(
    total_cellcount = n(),
    largenuc_cellcount = sum(nuclear_size == "large")
  ) %>%
  ungroup() %>%
  mutate(largenuc_pct = largenuc_cellcount / total_cellcount * 100) %>%
  mutate(genotype = fct_relevel(genotype, c("esg", "toll", "cactus")))

stat <- df %>%
  tukey_hsd(largenuc_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = largenuc_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "large nuclei cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "skyblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    cactus = expression(Cactus^"RNAi")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_05/esg-toll-cactus_largenuc.pdf", width = 5.5, height = 5)
```

### Large GFP + per total large cells

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype) %>%
  summarise(
    total_cellcount = n(),
    largenuc_cellcount = sum(nuclear_size == "large"),
    largenuc_GFPpos_cellcount = sum(nuclear_size == "large" & GFP_positive == TRUE)
  ) %>%
  ungroup() %>%
  mutate(largenuc_GFPpos_pct = largenuc_GFPpos_cellcount / largenuc_cellcount * 100) %>%
  mutate(genotype = fct_relevel(genotype, c("esg", "toll", "cactus")))

stat <- df %>%
  tukey_hsd(largenuc_GFPpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = largenuc_GFPpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "GFP+ large nuclei cells / Large cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "skyblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    cactus = expression(Cactus^"RNAi")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_05/esg-toll-cactus_largenuc-and-GFPpos.pdf", width = 5.5, height = 5)
```

### Small cells per total

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype) %>%
  summarise(
    total_cellcount = n(),
    smallnuc_cellcount = sum(nuclear_size == "small")
  ) %>%
  ungroup() %>%
  mutate(smallnuc_pct = smallnuc_cellcount / total_cellcount * 100) %>%
  mutate(genotype = fct_relevel(genotype, c("esg", "toll", "cactus")))

stat <- df %>%
  tukey_hsd(smallnuc_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = smallnuc_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Small nuclei cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "skyblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    cactus = expression(Cactus^"RNAi")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_05/esg-toll-cactus_smallnuc.pdf", width = 5.5, height = 5)

```

### Small GFP + per total small cells

```{r}
##
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype) %>%
  summarise(
    total_cellcount = n(),
    smallnuc_cellcount = sum(nuclear_size == "small"),
    smallnuc_GFPpos_cellcount = sum(nuclear_size == "small" & GFP_positive == TRUE)
  ) %>%
  ungroup() %>%
  filter(!str_detect(filename, "22d")) %>%
  mutate(smallnuc_GFPpos_pct = smallnuc_GFPpos_cellcount / smallnuc_cellcount * 100) %>%
  mutate(genotype = fct_relevel(genotype, c("esg", "toll", "cactus")))

stat <- df %>%
  tukey_hsd(smallnuc_GFPpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = smallnuc_GFPpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "GFP+ small nuclei cells / small cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.adj.signif}") +
  scale_fill_manual(values = c("gray60", "coral", "skyblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b"),
    cactus = expression(Cactus^"RNAi")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_05/esg-toll-cactus_smallnuc-and-GFPpos.pdf", width = 5.5, height = 5)
```

## Bsk control folder 06

### Data wrangling

```{r}
##
df_annotated <- process_files("/Users/jefflee/Desktop/for_ash_13sep/bsk control/1/output_df", "expA")

## Set nuclear size threshold
df_annotated %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = axis_major_length)) + 
  geom_vline(xintercept = 7, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 14, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 17.5, linetype = "dashed", alpha = 0.5) + 
  geom_density() + 
  theme_bw() +
  facet_wrap(~ experiment + age)

df_nucsize <- df_annotated %>%
  filter(axis_major_length > 2) %>%
  mutate(nuclear_size = if_else(axis_major_length > 17.5, "large", "small"))

## Set GFP threshold
esg_GFP_control <- df_nucsize %>%
  filter(genotype == "esg") %>%
  group_by(experiment, nuclear_size, age) %>%
  summarise(esg_GFP_density = mean(GFP_intensity_density, na.rm = TRUE)) %>%
  ungroup()

df_GFPnorm <- df_nucsize %>%
  left_join(esg_GFP_control, by = c("experiment", "nuclear_size", "age")) %>%
  mutate(norm_GFP_intensity_density = GFP_intensity_density / esg_GFP_density) %>%
  mutate(genotype = fct_relevel(genotype, c("esg", "toll", "bsk"))) %>%
  mutate(nuclear_size = fct_relevel(nuclear_size, c("small", "large")))

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density)) +
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = 2) + 
  facet_wrap(~ experiment) 

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density, y = axis_major_length)) +
  geom_point() + 
  geom_vline(xintercept = 1.25) + 
  facet_wrap(~ experiment) 

df_GFPnorm_thresholded <- df_GFPnorm %>%
#   filter(!(nuclear_size == "small" & norm_GFP_intensity_density < 1.25)) %>%
  mutate(GFP_positive = if_else(norm_GFP_intensity_density > 1.5, TRUE, FALSE))

```

### GFP+ cells per total cells 

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive)
  ) %>%
  ungroup() %>%
  mutate(GFPpos_pct = GFPpos_cellcount / total_cellcount * 100) 

stat <- df %>%
  t_test(GFPpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = GFPpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Bsk control GFP+ cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "steelblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    bsk = expression(Bsk^"DN")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_06/bsk-control_GFPpos.pdf", width = 5.5, height = 5)
```

### Large cells per total

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    largenuc_cellcount = sum(nuclear_size == "large")
  ) %>%
  ungroup() %>%
  mutate(largenuc_pct = largenuc_cellcount / total_cellcount * 100) 

stat <- df %>%
  t_test(largenuc_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = largenuc_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Bsk control large nuclei cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "steelblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    bsk = expression(Bsk^"DN")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_06/bsk-control_largenuc.pdf", width = 5.5, height = 5)
```

### Small cells per total

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    smallnuc_cellcount = sum(nuclear_size == "small")
  ) %>%
  ungroup() %>%
  mutate(smallnuc_pct = smallnuc_cellcount / total_cellcount * 100) 

stat <- df %>%
  t_test(smallnuc_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = smallnuc_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Bsk control small nuclei cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "steelblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    bsk = expression(Bsk^"DN")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_06/bsk-control_smallnuc.pdf", width = 5.5, height = 5)
```

### Total cell count

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    smallnuc_cellcount = sum(nuclear_size == "small")
  ) %>%
  ungroup() %>%
  mutate(smallnuc_pct = smallnuc_cellcount / total_cellcount * 100) 

stat <- df %>%
  t_test(total_cellcount ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = total_cellcount, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Bsk control total cell counts per image",
    x = "Genotype",
    y = "Cell count"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "steelblue")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    bsk = expression(Bsk^"DN")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_06/bsk-control_total-cellcount.pdf", width = 5.5, height = 5)
```

\newpage


## ISC folder 07 

### Data wrangling

```{r}
##
output_files_A <- list.files(
    "/Users/jefflee/Desktop/for_ash_13sep/ISC/1/output_df",
    pattern = "*.csv", 
    full.names = TRUE) %>%
  set_names(~basename(.x) %>% tools::file_path_sans_ext())

output_files_B <- list.files(
    "/Users/jefflee/Desktop/for_ash_13sep/ISC/2/output_df",
    pattern = "*.csv", 
    full.names = TRUE) %>%
  set_names(~basename(.x) %>% tools::file_path_sans_ext())

df_annotated_A <- output_files_A %>%
  future_map_dfr(~ read_csv(.x), .id = "filename", .progress = TRUE) %>% 
  janitor::clean_names() %>%
  dplyr::select(-x1) %>%
  mutate(genotype = case_when(
    str_detect(filename, "toll") ~ "toll",
    TRUE ~ "esg"
  )) %>%
  mutate(age = str_extract(filename, "[:digit:]+d")) %>%
  mutate(age = case_when(
    age == "22d" ~ "22d",
    TRUE ~ "12d"
  )) %>%
  mutate(GFP_intensity_density = gfp_intensity_sum / doughnut_area) %>%
  dplyr::rename("centroid_z" = centroid_0, "centroid_y" = centroid_1, "centroid_x" = centroid_2) %>%
  mutate(experiment = "expA") 

df_annotated_B <- output_files_B %>%
  future_map_dfr(~ read_csv(.x), .id = "filename", .progress = TRUE) %>% 
  janitor::clean_names() %>%
  dplyr::select(-x1) %>%
  mutate(genotype = case_when(
    str_detect(filename, "toll") ~ "toll",
    TRUE ~ "esg"
  )) %>%
  mutate(age = str_extract(filename, "[:digit:]+d")) %>%
  mutate(age = case_when(
    age == "22d" ~ "22d",
    TRUE ~ "12d"
  )) %>%
  mutate(GFP_intensity_density = gfp_intensity_sum / doughnut_area) %>%
  dplyr::rename("centroid_z" = centroid_0, "centroid_y" = centroid_1, "centroid_x" = centroid_2) %>%
  mutate(experiment = "expB") 

df_annotated <- bind_rows(df_annotated_A, df_annotated_B)

## Set nuclear size threshold
df_annotated %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = axis_major_length)) + 
  geom_vline(xintercept = 7, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 14, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 17.5, linetype = "dashed", alpha = 0.5) + 
  geom_density() + 
  theme_bw() +
  facet_wrap(~ experiment + age)

df_nucsize <- df_annotated %>%
  filter(axis_major_length > 2) %>%
  mutate(nuclear_size = if_else(axis_major_length > 17.5, "large", "small"))

## Set GFP threshold
esg_GFP_control <- df_nucsize %>%
  filter(genotype == "esg") %>%
  group_by(experiment, nuclear_size, age) %>%
  summarise(esg_GFP_density = mean(GFP_intensity_density, na.rm = TRUE)) %>%
  ungroup()

df_GFPnorm <- df_nucsize %>%
  left_join(esg_GFP_control, by = c("experiment", "nuclear_size", "age")) %>%
  mutate(norm_GFP_intensity_density = GFP_intensity_density / esg_GFP_density) %>%
  mutate(genotype = fct_relevel(genotype, c("esg", "toll", "bsk"))) %>%
  mutate(nuclear_size = fct_relevel(nuclear_size, c("small", "large")))

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density)) +
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = 2) + 
  facet_wrap(~ experiment) 

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density, y = axis_major_length)) +
  geom_point() + 
  geom_vline(xintercept = 1.25) + 
  facet_wrap(~ experiment) 

df_GFPnorm_thresholded <- df_GFPnorm %>%
#   filter(!(nuclear_size == "small" & norm_GFP_intensity_density < 1.25)) %>%
  mutate(GFP_positive = if_else(norm_GFP_intensity_density > 1.5, TRUE, FALSE))

```

### GFP+ cells / total cells

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive)
  ) %>%
  ungroup() %>%
  mutate(GFPpos_pct = GFPpos_cellcount / total_cellcount * 100) 

stat <- df %>%
  t_test(GFPpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = GFPpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "ISC GFP+ cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "coral")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_07/esg_toll_GFPpos.pdf", width = 5.5, height = 5)
```

### Total cells 

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive)
  ) %>%
  ungroup() %>%
  mutate(GFPpos_pct = GFPpos_cellcount / total_cellcount * 100) 

stat <- df %>%
  t_test(total_cellcount ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = total_cellcount, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "ISC Total cells",
    x = "Genotype",
    y = "Cell count"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "coral")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_07/esg_toll_total-cellcount.pdf", width = 5.5, height = 5)
```

## Dif RNAi folder 08

### Data wrangling

```{r}
##
df_annotated <- process_files("/Users/jefflee/Desktop/for_ash_13sep/difrnai/1/output_df", "expA") %>%
  mutate(genotype = if_else(genotype == "NA", "dif", genotype))

## Set nuclear size threshold
df_annotated %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = axis_major_length)) + 
  geom_vline(xintercept = 7, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 14, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 17.5, linetype = "dashed", alpha = 0.5) + 
  geom_density() + 
  theme_bw() +
  facet_wrap(~ experiment + age)

df_nucsize <- df_annotated %>%
  filter(axis_major_length > 2) %>%
  mutate(nuclear_size = if_else(axis_major_length > 17.5, "large", "small"))

## Set GFP threshold
esg_GFP_control <- df_nucsize %>%
  filter(genotype == "esg") %>%
  group_by(experiment, nuclear_size, age) %>%
  summarise(esg_GFP_density = mean(GFP_intensity_density, na.rm = TRUE)) %>%
  ungroup()

df_GFPnorm <- df_nucsize %>%
  left_join(esg_GFP_control, by = c("experiment", "nuclear_size", "age")) %>%
  mutate(norm_GFP_intensity_density = GFP_intensity_density / esg_GFP_density) %>%
  mutate(genotype = fct_relevel(genotype, c("esg", "toll", "bsk"))) %>%
  mutate(nuclear_size = fct_relevel(nuclear_size, c("small", "large")))

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density)) +
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = 2) + 
  facet_wrap(~ experiment) 

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density, y = axis_major_length)) +
  geom_point() + 
  geom_vline(xintercept = 1.25) + 
  facet_wrap(~ experiment) 

df_GFPnorm_thresholded <- df_GFPnorm %>%
#   filter(!(nuclear_size == "small" & norm_GFP_intensity_density < 1.25)) %>%
  mutate(GFP_positive = if_else(norm_GFP_intensity_density > 1.5, TRUE, FALSE))
```

### GFPpos per total

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive)
  ) %>%
  ungroup() %>%
  mutate(GFPpos_pct = GFPpos_cellcount / total_cellcount * 100) 

stat <- df %>%
  t_test(GFPpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = GFPpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "GFP+ cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "magenta")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    dif = expression(Dif^"RNAi")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_08/esg_difrnai_GFPpos.pdf", width = 5.5, height = 5)
```

### Large per total

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    largenuc_cellcount = sum(nuclear_size == "large")
  ) %>%
  ungroup() %>%
  mutate(largenuc_pct = largenuc_cellcount / total_cellcount * 100) 

stat <- df %>%
  t_test(largenuc_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = largenuc_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Large nuclear cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "magenta")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    dif = expression(Dif^"RNAi")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_08/esg_difrnai_largenuc.pdf", width = 5.5, height = 5)
```

### Small per total

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    smallnuc_cellcount = sum(nuclear_size == "small")
  ) %>%
  ungroup() %>%
  mutate(smallnuc_pct = smallnuc_cellcount / total_cellcount * 100) 

stat <- df %>%
  t_test(smallnuc_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = smallnuc_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Small nuclear cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "magenta")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    dif = expression(Dif^"RNAi")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_08/esg_difrnai_smallnuc.pdf", width = 5.5, height = 5)
```

### Total cells

```{r}
df <- df_GFPnorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    smallnuc_cellcount = sum(nuclear_size == "small")
  ) %>%
  ungroup() %>%
  mutate(smallnuc_pct = smallnuc_cellcount / total_cellcount * 100) 

stat <- df %>%
  t_test(total_cellcount ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = total_cellcount, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "Total cells",
    x = "Genotype",
    y = "Cell count"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "magenta")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    dif = expression(Dif^"RNAi")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_08/esg_difrnai_total-cellcount.pdf", width = 5.5, height = 5)
```

## Dllacz folder 09

### Data wrangling

```{r}
##
df_annotated_A <- process_files("/Users/jefflee/Desktop/for_ash_13sep/dllacz/1/output_df", "expA") %>%
  mutate(dllacz_intensity_density = other_intensity_sum / area)

df_annotated_B <- process_files("/Users/jefflee/Desktop/for_ash_13sep/dllacz/2/output_df", "expB") %>%
  mutate(dllacz_intensity_density = other_intensity_sum / area)

df_annotated <- bind_rows(df_annotated_A, df_annotated_B)

## Set nuclear size threshold
df_annotated %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = axis_major_length)) + 
  geom_vline(xintercept = 7, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 14, linetype = "dashed", alpha = 0.5) + 
  geom_vline(xintercept = 17.5, linetype = "dashed", alpha = 0.5) + 
  geom_density() + 
  theme_bw() +
  facet_wrap(~ experiment + age)

df_nucsize <- df_annotated %>%
  filter(axis_major_length > 2) %>%
  mutate(nuclear_size = if_else(axis_major_length > 17.5, "large", "small"))

## Set GFP threshold
esg_GFP_control <- df_nucsize %>%
  filter(genotype == "esg") %>%
  group_by(experiment, nuclear_size, age) %>%
  summarise(esg_GFP_density = mean(GFP_intensity_density, na.rm = TRUE)) %>%
  ungroup()

df_GFPnorm <- df_nucsize %>%
  left_join(esg_GFP_control, by = c("experiment", "nuclear_size", "age")) %>%
  mutate(norm_GFP_intensity_density = GFP_intensity_density / esg_GFP_density) %>%
  mutate(genotype = fct_relevel(genotype, c("esg", "toll", "bsk"))) %>%
  mutate(nuclear_size = fct_relevel(nuclear_size, c("small", "large")))

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density)) +
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = 2) + 
  facet_wrap(~ experiment) 

df_GFPnorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_GFP_intensity_density, y = axis_major_length)) +
  geom_point() + 
  geom_vline(xintercept = 1.25) + 
  facet_wrap(~ experiment) 

df_GFPnorm_thresholded <- df_GFPnorm %>%
  filter(!(nuclear_size == "small" & norm_GFP_intensity_density < 1.25)) %>%
  mutate(GFP_positive = if_else(norm_GFP_intensity_density > 1.5, TRUE, FALSE))

## Set dllacz threshold
esg_dllacz_control <- df_GFPnorm_thresholded %>%
  filter(genotype == "esg") %>%
  group_by(experiment, nuclear_size, age) %>%
  summarise(esg_dllacz_density = mean(dllacz_intensity_density, na.rm = TRUE)) %>%
  ungroup()

df_dllacznorm <- df_GFPnorm_thresholded %>%
  left_join(esg_dllacz_control, by = c("experiment", "nuclear_size", "age")) %>%
  mutate(norm_dllacz_intensity_density = dllacz_intensity_density / esg_dllacz_density) %>%
  mutate(genotype = fct_relevel(genotype, c("esg", "toll", "bsk"))) %>%
  mutate(nuclear_size = fct_relevel(nuclear_size, c("small", "large")))

df_dllacznorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_dllacz_intensity_density)) +
  geom_histogram(bins = 100) + 
  geom_vline(xintercept = 2) + 
  facet_wrap(~ experiment) 

df_dllacznorm %>%
  filter(age == "12d") %>%
  filter(genotype == "esg") %>%
  ggplot(aes(x = norm_dllacz_intensity_density, y = axis_major_length)) +
  geom_point() + 
  geom_vline(xintercept = 1.5) + 
  facet_wrap(~ experiment) 

df_dllacznorm_thresholded <- df_dllacznorm %>%
  mutate(dllacz_positive = if_else(norm_dllacz_intensity_density > 1.5, TRUE, FALSE))
```

### Dl+ cells per total

```{r}
df <- df_dllacznorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive),
    dllaczpos_cellcount = sum(dllacz_positive),
    dllaczpos_GFPpos_cellcount = sum(dllacz_positive == TRUE & GFP_positive == TRUE),
    dllaczpos_GFPneg_cellcount = sum(dllacz_positive == TRUE & GFP_positive == FALSE),
  ) %>%
  ungroup() %>%
  mutate(
    GFPpos_pct = GFPpos_cellcount / total_cellcount * 100,
    dllaczpos_pct = dllaczpos_cellcount / total_cellcount * 100,
    dllaczpos_GFPpos_pct = dllaczpos_GFPpos_cellcount / total_cellcount * 100,
    dllaczpos_GFPneg_pct = dllaczpos_GFPneg_cellcount / total_cellcount * 100,
    ) 

stat <- df %>%
  t_test(dllaczpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = dllaczpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "LacZ+ cells / Total cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "coral")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_09/dllaczpos-per-totalcells.pdf", width = 5.5, height = 5)
```

### Dl+ cells per total GFP+ cells

```{r}
df <- df_dllacznorm_thresholded %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive),
    dllaczpos_cellcount = sum(dllacz_positive),
    dllaczpos_GFPpos_cellcount = sum(dllacz_positive == TRUE & GFP_positive == TRUE),
    dllaczpos_GFPneg_cellcount = sum(dllacz_positive == TRUE & GFP_positive == FALSE),
  ) %>%
  ungroup() %>%
  mutate(
    GFPpos_pct = GFPpos_cellcount / total_cellcount * 100,
    dllaczpos_pct_of_GFPpos = dllaczpos_GFPpos_cellcount / GFPpos_cellcount * 100,
    dllaczpos_GFPpos_pct = dllaczpos_GFPpos_cellcount / total_cellcount * 100,
    dllaczpos_GFPneg_pct = dllaczpos_GFPneg_cellcount / total_cellcount * 100,
    ) 

stat <- df %>%
  t_test(dllaczpos_pct_of_GFPpos ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = dllaczpos_pct_of_GFPpos, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "LacZ+ & GFP+ cells / GFP+ cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "coral")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_09/dllaczpos-GFPpos-per-GFPpos.pdf", width = 5.5, height = 5)
```

### Dl+ cells per small nuclei cells

```{r}
df <- df_dllacznorm_thresholded %>%
  filter(nuclear_size == "small") %>%
  group_by(filename, genotype, experiment) %>%
  summarise(
    total_cellcount = n(),
    GFPpos_cellcount = sum(GFP_positive),
    dllaczpos_cellcount = sum(dllacz_positive),
    dllaczpos_GFPpos_cellcount = sum(dllacz_positive == TRUE & GFP_positive == TRUE),
    dllaczpos_GFPneg_cellcount = sum(dllacz_positive == TRUE & GFP_positive == FALSE),
  ) %>%
  ungroup() %>%
  mutate(
    GFPpos_pct = GFPpos_cellcount / total_cellcount * 100,
    dllaczpos_pct = dllaczpos_cellcount / total_cellcount * 100,
    dllaczpos_GFPpos_pct = dllaczpos_GFPpos_cellcount / total_cellcount * 100,
    dllaczpos_GFPneg_pct = dllaczpos_GFPneg_cellcount / total_cellcount * 100,
    ) 

stat <- df %>%
  t_test(dllaczpos_pct ~ genotype) %>%
  add_significance() %>%
  add_xy_position()

df %>%
  ggplot(aes(x = genotype, y = dllaczpos_pct, fill = genotype)) +
  geom_boxplot(width = 0.5) +
  labs(
    title = "LacZ+ cells / Small nuclei cells",
    x = "Genotype",
    y = "Percentage of cells"
  ) + 
  add_pvalue(data = stat, 
             inherit.aes = FALSE,
             label = "{p.signif}") +
  scale_fill_manual(values = c("gray60", "coral")) + 
  scale_x_discrete(labels = c(
    esg = expression(W^1118),
    toll = expression(Toll^"10b")
  )) + 
  theme_bw(base_size = 10) +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "none"
    )

ggsave("./plots/plots_Sep2023_09/dllaczpos-per-smallnuc-cellcount.pdf", width = 5.5, height = 5)
```







